---
title: "Meta-Analysis_TMS_Physical_Activity"
author: "IM Lahart, A Farajzadeh, MP Boisgontier"
date: "`r format(Sys.Date(),'%e de %B, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
---
<style>
body{
  font-size: 8pt;
}
</style>
---

# R Markdown file set-up and packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages required:
1) dmetar
2) tidyverse
3) meta
4) metafor
5) esc
6) TOSTER


```{r install and load dmetar, include=FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
```

```{r packages, include=FALSE}
#Install tidyverse package if needed for 'glimpse'
if(!require(tidyverse)){install.packages('tidyverse')}
#Load tidyverse package
library(tidyverse)

#Install meta package if needed for meta-analysis
if(!require(meta)){install.packages('meta')}
#Load meta package
library(meta)

#Install metafor package if needed for meta-analysis
if(!require(metafor)){install.packages('metafor')}
#Load metfor package
library(metafor)

#Install esc package if needed for Fisher z conversion to r
if(!require(esc)){install.packages('esc')}
#Load esc package
library(esc)

#Install TOSTER package if needed for equivalence testing
if(!require(TOSTER)){install.packages('TOSTER')}
#Load TOSTER package
library(TOSTER)

#Install svglite package if needed for svg output
if(!require(svglite)){install.packages('svglite')}
#Load svglite package
library(svglite)

```


# Meta-analysis
# Import Pearson r data
```{r import data files, include=FALSE}
excitability_r  <- read.csv("excitability_r.csv",  header = TRUE, sep = ",")
inhibition_r <- read.csv("inhibition_r.csv", header = TRUE, sep = ",")
facilitation_r <- read.csv("facilitation_r.csv", header = TRUE, sep = ",")
```

# Data file glimpse
```{r glimpse, include=FALSE}
glimpse(excitability_r)
glimpse(inhibition_r)
glimpse(facilitation_r)
```

# Calculating z and var.z 
```{r z and var.z calculation, include=FALSE}
excitability_r$z <- atanh(excitability_r$cor)
excitability_r$var.z <- 1/(excitability_r$n - 3)
excitability_r$cor_id <- 1:nrow(excitability_r)
write.csv(excitability_r, "excitability_r.csv", row.names = FALSE)
unique(excitability_r)

inhibition_r$z <- atanh(inhibition_r$cor)
inhibition_r$var.z <- 1/(inhibition_r$n - 3)
inhibition_r$cor_id <- 1:nrow(inhibition_r)
write.csv(inhibition_r, "inhibition_r.csv", row.names = FALSE)
unique(inhibition_r)

facilitation_r$z <- atanh(facilitation_r$cor)
facilitation_r$var.z <- 1/(facilitation_r$n - 3)
facilitation_r$cor_id <- 1:nrow(facilitation_r)
write.csv(facilitation_r, "facilitation_r.csv", row.names = FALSE)
unique(facilitation_r)
```

## Excitability (CSE): Primary analysis of using metafor::rma.mv()
```{r primary excitability meta-analysis RE REML using metafor}
m.cor.excitability <- rma.mv(yi = z, # pool correlation coefficients Fishers Z transformation https://bookdown.org/mwheymans/bookmi/pooling-correlation-coefficients-1.html
                V = var.z, # sampling variance of Fisher's Z values: 1/(N−3), where N = the sample size.
                slab = author,
                data = excitability_r,
                random = ~ 1 | author/cor_id,
                test = "t", 
                method = "REML")
summary(m.cor.excitability)
```

### Excitability (CSE): Converting Fisher's z back to Pearson's r

```{r Convert excitability Fisher z back to Pearsons r}
round(convert_z2r(-0.0287), 2) # point estimate
round(convert_z2r(-0.1190), 2) # lower CI
round(convert_z2r(0.0617), 2) # Upper CI
```

### Excitability (CSE): Explore heterogeneity

```{r excitability Heterogeneity}
i2 <- var.comp(m.cor.excitability)
summary(i2)
plot(i2)
```

ADD TEXT


## Excitability (CSE): Sensitivity analysis using meta::metacor()

```{r Primary excitability analysis using meta}
m.excitability <- metacor(cor = cor, 
              n = n,
              studlab = author,
              data = excitability_r,
              cluster = cluster,
              common = FALSE,
              random = TRUE,
              method.tau = "REML",
              method.random.ci = "HK",
              title = "Sensitivity meta-analysis using metacor")

m.excitability
```


#Corticospinal excitability
ADD TEXT

## Excitability (CSE): Forest plot
```{r Forest plot excitability, fig.height=7, fig.width=14}
forest(m.excitability, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```


Excitability (CSE): Save plot
```{r Forest plot excitability export SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_excitability.svg", height = 7, width = 7)

forest(m.excitability, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

## Inhibition (SICI, LICI, cSP, iSP): Primary analysis of using metafor::rma.mv()
```{r primary inhibition meta-analysis RE REML using metafor}
m.cor.inhibition <- rma.mv(yi = z, # pool correlation coefficients Fishers Z transformation https://bookdown.org/mwheymans/bookmi/pooling-correlation-coefficients-1.html
                V = var.z, # sampling variance of Fisher's Z values: 1/(N−3), where N = the sample size.
                slab = author,
                data = inhibition_r,
                random = ~ 1 | author/cor_id,
                test = "t", 
                method = "REML")
summary(m.cor.inhibition)
```

### Inhibition (SICI, LICI, cSP, iSP): Converting Fisher's z back to Pearson's r

```{r Convert inhibition Fisher z back to Pearsons r}
round(convert_z2r(0.0237), 2) # point estimate
round(convert_z2r(-0.1021), 2) # lower CI
round(convert_z2r(0.1496), 2) # Upper CI
```

### Inhibition (SICI, LICI, cSP, iSP): Explore heterogeneity

```{r inhibition Heterogeneity}
i2 <- var.comp(m.cor.inhibition)
summary(i2)
plot(i2)
```

ADD TEXT


## Inhibition (SICI, LICI, cSP, iSP): Sensitivity analysis using meta::metacor()

```{r Primary inhibition analysis using meta}
m.inhibition <- metacor(cor = cor, 
              n = n,
              studlab = author,
              data = inhibition_r,
              cluster = cluster,
              common = FALSE,
              random = TRUE,
              method.tau = "REML",
              method.random.ci = "HK",
              title = "Sensitivity meta-analysis using metacor")

m.inhibition
```

#Cortical inhibition
ADD TEXT

## Inhibition (SICI, LICI, cSP, iSP): Forest plot
```{r Forest plot for inhibition, fig.height=7, fig.width=14}
forest(m.inhibition, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```


Inhibition (SICI, LICI, cSP, iSP): Save plot
```{r Forest plot inhibition export SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_inhibition.svg", height = 7, width = 7)

forest(m.inhibition, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```


## Facilitation (ICF, SICF): Primary analysis of using metafor::rma.mv()
```{r primary facilitation meta-analysis RE REML using metafor}
m.cor.facilitation <- rma.mv(yi = z, # pool correlation coefficients Fishers Z transformation https://bookdown.org/mwheymans/bookmi/pooling-correlation-coefficients-1.html
                V = var.z, # sampling variance of Fisher's Z values: 1/(N−3), where N = the sample size.
                slab = author,
                data = facilitation_r,
                random = ~ 1 | author/cor_id,
                test = "t", 
                method = "REML")
summary(m.cor.facilitation)
```

### Facilitation (ICF, SICF): Converting Fisher's z back to Pearson's r

```{r Convert facilitation Fisher z back to Pearsons r}
round(convert_z2r(0.0674), 2) # point estimate
round(convert_z2r(-0.0449), 2) # lower CI
round(convert_z2r(0.1797), 2) # Upper CI
```

### Facilitation (ICF, SICF): Explore heterogeneity

```{r facilitation Heterogeneity}
i2 <- var.comp(m.cor.facilitation)
summary(i2)
plot(i2)
```

ADD TEXT


## Facilitation (ICF, SICF): Sensitivity analysis using meta::metacor()

```{r Primary facilitation analysis using meta}
m.facilitation <- metacor(cor = cor, 
              n = n,
              studlab = author,
              data = facilitation_r,
              cluster = cluster,
              common = FALSE,
              random = TRUE,
              method.tau = "REML",
              method.random.ci = "HK",
              title = "Sensitivity meta-analysis using metacor")

m.facilitation
```

#Cortical Facilitation
ADD TEXT

## Facilitation (ICF, SICF): Forest plot
```{r Forest plot facilitation, fig.height=7, fig.width=14}
forest(m.facilitation, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```


Facilitation (ICF, SICF): Save plot
```{r Forest plot facilitation export SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_facilitation.svg", height = 7, width = 7)

forest(m.facilitation, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

# Meta-analysis: Subgroup analyses
## Inhibition measure
```{r Subgroup analysis by inhibitory measure using metafor}
inhibition_r$inhibitory.measure <- as.factor(inhibition_r$inhibitory.measure)

inhibition_tms_subg <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = inhibition_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ inhibitory.measure)

summary(inhibition_tms_subg)
```

ADD TEXT


```{r inhibition by measure type meta, warning=FALSE}
inhibition_measure_type <- update(m.inhibition, subgroup = inhibitory.measure, tau.common = TRUE)
inhibition_measure_type
```

ADD TEXT

```{r Forest plot for inhibition type using meta, fig.height=10, fig.width=14}
forest(inhibition_measure_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```

Inhibition measure type: Save plot
```{r Forest plot inhibition type export SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_inhibition-measure.svg", height = 10, width = 14)

forest(inhibition_measure_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

## Facilitation Measure

```{r Subgroup analysis by facilitation type using metafor}
facilitation_r$facilitatory.measure <- as.factor(facilitation_r$facilitatory.measure)

facilitation_type <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = facilitation_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ facilitatory.measure)

summary(facilitation_type)
```


```{r facilitation type meta, warning=FALSE}
facilitation_measure_type <- update(m.facilitation, subgroup = facilitatory.measure, tau.common = TRUE)
facilitation_measure_type
```


```{r Forest plot for facilitation type meta, fig.height=7, fig.width=14}

forest(facilitation_measure_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```

Facilitation by tms measure type: Save plot
```{r Forest plot facilitation type SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_facilitation-type.svg", height = 7, width = 14)

forest(facilitation_measure_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

## Physical Activity Objectivity for Excitability

```{r Subgroup analysis by physical activity objectivity for excitability using metafor}
excitability_r$PA_objectivity <- as.factor(excitability_r$PA_objectivity)

excitability_PA_type <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = excitability_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ PA_objectivity)

summary(excitability_PA_type)
```


```{r excitability PA type meta, warning=FALSE}
excitability_PA_type <- update(m.excitability, subgroup = PA_objectivity, tau.common = TRUE)
excitability_PA_type
```


```{r Forest plot by physical activity objectivity for excitability using meta, fig.height=7, fig.width=14}

forest(excitability_PA_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```

excitability by PA measure type: Save plot
```{r Forest plot excitability PA type SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_excitability-PA-type.svg", height = 7, width = 14)

forest(excitability_PA_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

## Physical Activity Objectivity for Inhibition

```{r Subgroup analysis by physical activity objectivity for inhibition using metafor}
inhibition_r$PA_objectivity <- as.factor(inhibition_r$PA_objectivity)

inhibition_PA_type <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = inhibition_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ PA_objectivity)

summary(inhibition_PA_type)
```

```{r inhibition PA type meta, warning=FALSE}
inhibition_PA_type <- update(m.inhibition, subgroup = PA_objectivity, tau.common = TRUE)
inhibition_PA_type
```


```{r Forest plot by physical activity objectivity for inhibition using meta, fig.height=7, fig.width=14}

forest(inhibition_PA_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```

Inhibition by PA measure type: Save plot
```{r Forest plot inhibition PA type SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_inhibition-PA-type.svg", height = 7, width = 14)

forest(inhibition_PA_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

## Physical Activity Objectivity for Facilitation

```{r Subgroup analysis by physical activity objectivity for facilitation using metafor}
facilitation_r$PA_objectivity <- as.factor(facilitation_r$PA_objectivity)

facilitation_PA_type <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = facilitation_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ PA_objectivity)

summary(facilitation_PA_type)
```

```{r facilitation PA type meta, warning=FALSE}
facilitation_PA_type <- update(m.facilitation, subgroup = PA_objectivity, tau.common = TRUE)
facilitation_PA_type
```

```{r Forest plot by physical activity objectivity for facilitation using meta, fig.height=7, fig.width=14}

forest(facilitation_PA_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```

Facilitation by tms measure type: Save plot
```{r Forest plot facilitation PA type SVG, echo=TRUE}

library(svglite)

svglite("forest_plot_facilitation-type.svg", height = 7, width = 14)

forest(facilitation_PA_type, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-0.9,0.9), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()

```

# Meta Regressions
## Excitability
### Meta-regressions by proportion of women
```{r Meta-regression by proportion of women excitability}
m.cor.reg.excitability.women <- metareg(m.excitability, ~Prop_women)
m.cor.reg.excitability.women
```

### Meta-regressions by age
```{r Meta-regression by age excitability}
m.cor.reg.excitability.age <- metareg(m.excitability, ~Age)
m.cor.reg.excitability.age
```

### Meta-regressions by study quality
```{r Meta-regression by study quality excitability}
m.cor.reg.excitability.quality <- metareg(m.excitability, ~Q_score)
m.cor.reg.excitability.quality
```

## Inhibition
### Meta-regressions by proportion of women
```{r Meta-regression by proportion of women inhibition}
m.cor.reg.inhibition.women <- metareg(m.inhibition, ~Prop_women)
m.cor.reg.inhibition.women
```

### Meta-regressions by age
```{r Meta-regression by age inhibition}
m.cor.reg.inhibition.age <- metareg(m.inhibition, ~Age)
m.cor.reg.inhibition.age
```

### Meta-regressions by study quality
```{r Meta-regression by study quality inhibition}
m.cor.reg.inhibition.quality <- metareg(m.inhibition, ~Q_score)
m.cor.reg.inhibition.quality
```

## Facilitation
### Meta-regressions by proportion of women
```{r Meta-regression by proportion of women facilitation}
m.cor.reg.facilitation.women <- metareg(m.facilitation, ~Prop_women)
m.cor.reg.facilitation.women
```

### Meta-regressions by age
```{r Meta-regression by age facilitation}
m.cor.reg.facilitation.age <- metareg(m.facilitation, ~Age)
m.cor.reg.facilitation.age
```

### Meta-regressions by study quality
```{r Meta-regression by study quality facilitation}
m.cor.reg.facilitation.quality <- metareg(m.facilitation, ~Q_score)
m.cor.reg.facilitation.quality
```

# Equivalence Testing
## Excitability
```{r Equivalence testing excitability}

# Define SESOI in r
sesoi_r <- 0.1

# Convert r to Fisher's z
low_eq_z  <- atanh(-sesoi_r)
high_eq_z <- atanh( sesoi_r)

TOSTmeta(
  ES = -0.0287,
  se = 0.0432,
  low_eqbound  = low_eq_z,
  high_eqbound =  high_eq_z,
  alpha = 0.05
)
```
## Inhibition
```{r Equivalence testing inhibition}

# Define SESOI in r
sesoi_r <- 0.1

# Convert r to Fisher's z
low_eq_z  <- atanh(-sesoi_r)
high_eq_z <- atanh( sesoi_r)

TOSTmeta(
  ES = 0.0237,
  se = 0.0597,
  low_eqbound  = low_eq_z,
  high_eqbound =  high_eq_z,
  alpha = 0.05
)
```


## Facilitation
```{r Equivalence testing facilitation}

# Define SESOI in r
sesoi_r <- 0.1

# Convert r to Fisher's z
low_eq_z  <- atanh(-sesoi_r)
high_eq_z <- atanh( sesoi_r)

TOSTmeta(
  ES = 0.0674,
  se = 0.0520,
  low_eqbound  = low_eq_z,
  high_eqbound =  high_eq_z,
  alpha = 0.05
)
```


# Publication bias analysis
## Small-study effects
### Funnel plot 

```{r Contour-enhanced funnel plot excitability, fig.height=6, fig.width=8}
# Define fill colors for contour
col.contour = c("gray85", "gray75")

# Funnel plot
meta::funnel(m.excitability, 
             xlim = c(-1.5, 1),
             contour = c(0.95, 0.99),
             col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (excitability)")
```

```{r Contour-enhanced funnel plot inhibition, fig.height=6, fig.width=8}
# Define fill colors for contour
col.contour = c("gray85", "gray75")

# Funnel plot
meta::funnel(m.inhibition, 
             xlim = c(-1.5, 1),
             contour = c(0.95, 0.99),
             col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (inhibition)")
```


```{r Save funnel plot}
png(file = "Funnel Plot.png", width = 2500, height = 2000, res = 300)

# Define fill colors for contour
col.contour = c("gray85", "gray75")

# Funnel plot
meta::funnel(m.inhibition, 
             xlim = c(-1.5, 1),
             contour = c(0.95, 0.99),
             col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (tms and Physical Activity)")

dev.off()
```

```{r Contour-enhanced funnel plot facilitation, fig.height=6, fig.width=8}
# Define fill colors for contour
col.contour = c("gray85", "gray75")

# Funnel plot
meta::funnel(m.facilitation, 
             xlim = c(-1.5, 1),
             contour = c(0.95, 0.99),
             col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (facilitation)")
```

### Egger's test
ADD TEXT

```{r Eggers test for excitability}
test.egger = rma.mv(z,var.z, mod = ~ sqrt(var.z), random =  ~ 1 | author/cor_id, data = excitability_r, test = "t")
test.egger
```


```{r Eggers test for inhibition}
test.egger = rma.mv(z,var.z, mod = ~ sqrt(var.z), random =  ~ 1 | author/cor_id, data = inhibition_r, test = "t")
test.egger
```


```{r Eggers test for facilitation}
test.egger = rma.mv(z,var.z, mod = ~ sqrt(var.z), random =  ~ 1 | author/cor_id, data = facilitation_r, test = "t")
test.egger
```
#Pulication Bias
ADD TEXT

# References
- Cohen J. Statistical power analysis for the behavioral sciences. 2nd ed.; 1988.  
- Egger M, Davey Smith G, Schneider M, Minder C. Bias in meta-analysis detected by a simple, graphical test. BMJ. 1997;315(7109):629-634. https://doi.org/10.1136/bmj.315.7109.62  
- Higgins JPT, Thompson SG. Quantifying heterogeneity in a meta-analysis. Stat Med. 2002;21(11):1539-1558. https://doi.org/10.1002/sim.1186 
- Knapp G, Hartung J. Improved tests for a random effects meta-regression with a single covariate. Stat Med. 2003;22(17):2693-2710. https://doi.org/10.1002/sim.1482  
- R Core Team. R: A language and environment for statistical computing [Computer software]. Version 4.3.1. Vienna, Austria: Foundation for Statistical Computing; 2023. https://www.r-project.org 
- Schwarzer G. Meta: General package for meta-analysis [R package]. Version 6.5-0; 2023. https://cran.r-project.org/web/packages/meta/meta.pdf 
- Simonsohn U, Nelson LD, Simmons JP. P-curve: A key to the file-drawer. J Exp Psychol Gen. 2014;143(2):534-547. http://doi.org/10.1037/a0033242  
- Viechtbauer W. Bias and efficiency of meta-analytic variance estimators in the random-effects model. J Educ Behav Stat. 2005;30(3):261-293. https://doi.org/10.3102/10769986030003261  
- Viechtbauer W. Conducting meta-analyses in R with the metafor package. J Stat Softw. 2010;36(3):1-48. https://doi.org/10.18637/jss.v036.i03  
- Viechtbauer W. Metafor: Meta-analysis package for R [R package]. Version 4.2-0; 2023. https://cran.r-pro-ject.org/web/packages/metafor/metafor.pdf  
- Viechtbauer, "W. (2023). Metafor: Meta-Analysis Package for R (Version 4.2-0) [R pakage]. https://cran.r-project.org/web/packages/metafor/metafor.pdf  