---
title: "Meta-Analysis_TMS_Physical_Activity"
author: "Ata Farajzadeh, Ian M. Lahart, Matthieu P.Boisgontier"
date: "`r format(Sys.Date(),'%e de %B, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
---
<style>
body{
  font-size: 8pt;
}
</style>
---

*R Markdown file set-up and packages*
Packages required:

(1) dmetar
(2) tidyverse
(3) meta
(4) metafor
(5) esc
(6) TOSTER
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
installed.packages()[, c("Package", "Version")]
```
```{r packages, include=FALSE}
# Source the package installation script
source("00_package_installation.R")

# Source custom functions
source("01_functions_preprocess.R")
source("02_functions_analysis.R")
source("03_functions_plots.R")
```

# Statistical Analyses
All analyses were conducted with R software (17) in RStudio statistical environment using metafor 
(18)  and  meta  packages  (19).  When  correlations  were  directly  reported,  these  values  were  extracted. 
When correlations were not reported, they were computed from available statistics (e.g., t-values, exact p-
values,  and  sample  sizes)  using  custom  R  scripts based  on  standard  relationships 
between test statistics and correlation coefficients. To ensure consistent interpretation across inhibitory
measures,  correlations  for  SICI  and  LICI  were  multiplied  by  −1  so  that  higher  values  consistently 
reflected stronger cortical inhibition across all measures.

## Primary Meta-Analyses
Pearson product–moment correlations from eligible studies were pooled to examine the relationship 
between physical activity and TMS measures of cortico-spinal excitability, cortical inhibition, and cortical 
facilitation.  Prior  to  analysis,  r  correlations  were  Fisher’s  z-transformed  to  stabilize  variance,  and  the 
corresponding sampling variances were calculated.

Meta-analyses  were  conducted  using  multilevel  random-effects  models  implemented  with  the 
metafor  package  (18).  This  approach  accounts  for  statistical  dependence  among  multiple  correlation 
estimates  reported  within  the  same  study.  A  multilevel  approach  was  used  because  several  studies 
contributed  more  than  one  correlation  estimate  (e.g.,  different  TMS  outcomes  or  measurement 
conditions),  which  introduces  statistical  dependence  among  effect  sizes.  Multilevel  meta-analysis 
appropriately accounts for this dependency without requiring aggregation of effect sizes within studies. 
Specifically, correlation estimates were nested within studies, resulting in a three-level model (level 1: 
sampling  variance,  level  2:  correlation  estimates  within  studies,  level  3:  studies).  Between-study 
heterogeneity was estimated using the restricted maximum likelihood estimator (20). Heterogeneity was 
quantified using the I² statistic, which represents the proportion of total variability in observed effect sizes 
that is not attributable to sampling error (21). Because a multilevel meta-analytic model was used, I² 
values were decomposed across variance components to estimate the proportion of variability attributable 
to differences between studies and between effect sizes within studies.

To  reduce  the  risk  of  inflated  type  I  error  rates,  confidence  intervals  for  pooled  estimates  were 
calculated  using  a  Knapp–Hartung  adjustment  (22).  In  addition  to  pooled  correlations  and  their 
confidence  intervals,  prediction  intervals  were  calculated  to  estimate  the  range  within  which  the  true 
effect size of a future study is expected to fall based on the current evidence. Unlike confidence intervals, 
which  describe  the  precision  of  the  pooled  estimate,  prediction  intervals  incorporate  between-study 
heterogeneity to reflect the expected variability of effects across future studies.

For visualization purposes, forest plots were produced using the meta package (19) with a RevMan 
layout. These plots were based on random-effects models equivalent to the multilevel analyses.

*Import Pearson r data*
```{r import data files, include=FALSE}
excitability_r <- import_correlation_data("excitability_r.csv")
inhibition_r <- import_correlation_data("inhibition_r.csv")
facilitation_r <- import_correlation_data("facilitation_r.csv")
```

*Data file glimpse*
```{r glimpse, include=FALSE}
glimpse(excitability_r)
glimpse(inhibition_r)
glimpse(facilitation_r)
```

*Calculating z and var.z*
```{r z and var.z calculation, include=FALSE}
excitability_r <- calculate_fisher_z(excitability_r)
inhibition_r <- calculate_fisher_z(inhibition_r)
facilitation_r <- calculate_fisher_z(facilitation_r)
```

*Excitability (CSE): Primary analysis of using metafor::rma.mv()*
```{r primary excitability meta-analysis RE REML using metafor}
m.cor.excitability <- run_multilevel_meta(excitability_r)
summary(m.cor.excitability)
```

*Excitability (CSE): Converting Fisher's z back to Pearson's r*
```{r Convert excitability Fisher z back to Pearsons r}
z_to_r(-0.0063)   # point estimate
z_to_r(-0.1239)   # lower CI
z_to_r(0.1113)    # Upper CI
```

*Excitability (CSE): Explore heterogeneity*
```{r excitability Heterogeneity}
i2_excitability <- var.comp(m.cor.excitability)
summary(i2_excitability)
plot(i2_excitability)
```

*Excitability (CSE): Sensitivity analysis using meta::metacor()*
```{r Primary excitability analysis using meta}
m.excitability <- run_sensitivity_meta(excitability_r, "Sensitivity meta-analysis: Excitability")
m.excitability
```

## Meta-Analysis
### Corticospinal Excitability
A total of 20 correlation estimates from 16 studies (600 participants) were included in the meta-
analysis examining the association between physical activity and corticospinal excitability. The multilevel 
random-effects  meta-analysis  indicated  no  significant  association  between  physical  activity  and 
corticospinal excitability (r = −0.03, 95% CI [−0.12, 0.06], p = 0.51) (Fig. 2). The prediction interval 
ranged from −0.12 to 0.07, indicating that future studies are expected to observe correlations ranging 
from  small  negative  to  small  positive  values.  Between-study  heterogeneity  was  negligible  (total  I²  = 
0.15%), with virtually no variance attributable to differences between studies. 


Subgroup analyses comparing physical activity measures (self-reported vs. device-based) showed no 
significant difference between measure types (Q = 0.28, p = 0.601). The pooled estimate was −0.05 (95% 
CI [−0.16, 0.07], k = 14) for self-reported measures and r = 0.00 (95% CI [−0.16, 0.17]; k = 6) for device-
based measures.

```{r Forest plot excitability, fig.height=7, fig.width=14}
create_forest_plot(m.excitability)
```
```{r Forest plot excitability export SVG, echo=TRUE}
save_forest_plot_svg(m.excitability, "forest_plot_excitability")
```
**Figure 2.** Forest plot of the association between physical activity and corticospinal 
excitability. Notes: IV = inverse variance, CI = confidence interval.

### Cortical Inhibition
A total of 18 correlation estimates from 14 studies (610 participants) were included in the meta-
analysis examining the association between habitual physical activity and measures of cortical inhibition. 
The multilevel random-effects meta-analysis indicated a significant positive association between physical 
activity and cortical inhibition (r = 0.02, 95% CI [−0.10, 0.15], p = 0.70) (Fig. 3). The prediction interval 
ranged from −0.31 to 0.35, indicating that future studies are expected to observe correlations ranging 
from  moderately  negative  to  moderately  positive  values.  Between-study  heterogeneity  was  moderate 
(total  I²  of  40.99%),  with  variability  occurring  almost  entirely  between  studies,  with  no  meaningful 
heterogeneity between effect sizes within studies. 

Subgroup analyses examining differences across inhibitory mechanisms (SICI, LICI, cSP, and iSP) 
revealed statistically significant differences between modulation types (Q = 5.71, p = 0.009) (Fig. 3). The 
association  was  significant  for  iSP  (r  =  0.47,  95%  CI  [0.21,  0.66];  k  =  2),  whereas  no  significant 
associations were observed for SICI (r = −0.07, 95% CI [−0.17, 0.04]; k = 13), LICI (r = 0.05, 95% CI 
[−0.28, 0.37]; k = 1), or cSP (r = 0.14, 95% CI [−0.16, 0.42]; k = 2).
Subgroup analyses comparing physical activity measures (self-reported vs. device-based) showed no 
significant difference between measure types (Q = 0.002, p = 0.888). The pooled estimate was r = 0.03 
(95% CI [−0.11, 0.17]; k = 16) for self-reported measures and −0.01 (95% CI [−0.41, 0.40]; k = 2) for 
device-based measures.

*Inhibition (SICI, LICI, cSP, iSP): Primary analysis of using metafor::rma.mv()*
```{r primary inhibition meta-analysis RE REML using metafor}
m.cor.inhibition <- run_multilevel_meta(inhibition_r)
summary(m.cor.inhibition)
```

*Inhibition (SICI, LICI, cSP, iSP): Converting Fisher's z back to Pearson's r*
```{r Convert inhibition Fisher z back to Pearsons r}
z_to_r(0.1642)   # point estimate
z_to_r(0.0429)   # lower CI
z_to_r(0.2856)   # Upper CI
```

*Inhibition (SICI, LICI, cSP, iSP): Explore heterogeneity*
```{r inhibition Heterogeneity}
i2_inhibition <- var.comp(m.cor.inhibition)
summary(i2_inhibition)
plot(i2_inhibition)
```

*Inhibition (SICI, LICI, cSP, iSP): Sensitivity analysis using meta::metacor()*
```{r Primary inhibition analysis using meta}
m.inhibition <- run_sensitivity_meta(inhibition_r, "Sensitivity meta-analysis: Inhibition")
m.inhibition
```

*Inhibition (SICI, LICI, cSP, iSP): Forest plot*
```{r Forest plot for inhibition, fig.height=7, fig.width=14}
create_forest_plot(m.inhibition)
```

*Inhibition (SICI, LICI, cSP, iSP): Save plot*
```{r Forest plot inhibition export SVG, echo=TRUE}
save_forest_plot_svg(m.inhibition, "forest_plot_inhibition")
```
**Figure 3.** Forest plot of the association between habitual physical activity and TMS 
measures of cortical inhibition. Notes: SICI = short-interval intracortical inhibition, LICI = 
long-interval intracortical inhibition, cSP = cortical silent period, iSP = ipsilateral silent 
period, IV = inverse variance, CI = confidence interval.

### Intracortical Facilitation
A  total  of  14  correlation  estimates  from  8  studies  (412  participants)  were  included  in  the  meta-
analysis  examining  the  association  between  habitual  physical  activity  and  TMS  measures  of  cortical 
facilitation. The multilevel random-effects meta-analysis indicated no statistically significant association 
between  physical  activity  and  cortical  facilitation  (r  =  0.07,  95%  CI  [−0.04,  0.18],  p  =  0.22).  The 
prediction interval ranged from −0.04 to 0.18, indicating that future studies would be expected to observe 
correlations ranging from slightly negative to small positive values. No meaningful heterogeneity was 
observed across studies (I² = 0%), indicating that variability in the observed correlations was entirely 
attributable to sampling error. Variance decomposition confirmed that neither between-study nor within-
study variance components contributed meaningfully to heterogeneity.


Subgroup analyses comparing facilitatory measures (ICF vs. SICF) showed no significant difference 
between measure types (Q = 0.002, p = 0.966) (Fig. 4). Point estimates were similar for ICF (r = 0.07, 
95% CI [−0.07, 0.21]; k = 9) and SICF (r = 0.06, 95% CI [−0.13, 0.25]; k = 5).

Subgroup analyses comparing physical activity measures (self-reported vs. device-based) showed no 
significant difference between measure types (Q = 0.59, p = 0.458). The pooled estimate for self-reported 
measures was r = 0.08 (95% CI [−0.04, 0.20]; k = 13), whereas only one study and there was only a single 
study using a device-based measure (r = −0.05, 95% CI [−0.37, 0.29]; k = 1).

*Facilitation (ICF, SICF): Primary analysis of using metafor::rma.mv()*
```{r primary facilitation meta-analysis RE REML using metafor}
m.cor.facilitation <- run_multilevel_meta(facilitation_r)
summary(m.cor.facilitation)
```

*Facilitation (ICF, SICF): Converting Fisher's z back to Pearson's r*
```{r Convert facilitation Fisher z back to Pearsons r}
z_to_r(0.0674)   # point estimate
z_to_r(-0.0449)  # lower CI
z_to_r(0.1797)   # Upper CI
```

*Facilitation (ICF, SICF): Explore heterogeneity*
```{r facilitation Heterogeneity}
i2_facilitation <- var.comp(m.cor.facilitation)
summary(i2_facilitation)
plot(i2_facilitation)
```

*Facilitation (ICF, SICF): Sensitivity analysis using meta::metacor()*
```{r Primary facilitation analysis using meta}
m.facilitation <- run_sensitivity_meta(facilitation_r, "Sensitivity meta-analysis: Facilitation")
m.facilitation
```

*Facilitation (ICF, SICF): Forest plot*
```{r Forest plot facilitation, fig.height=7, fig.width=14}
create_forest_plot(m.facilitation)
```

*Facilitation (ICF, SICF): Save plot*
```{r Forest plot facilitation export SVG, echo=TRUE}
save_forest_plot_svg(m.facilitation, "forest_plot_facilitation")
```
**Figure 4.** Forest plot of the association between habitual physical activity and 
transcranial magnetic stimulation measures of intracortical facilitation. Notes: ICF = 
intracortical facilitation, SICF = short-interval intracortical facilitation, IV = inverse 
variance, CI = confidence interval.

## Subgroup Meta-Analyses 
Subgroup analyses were conducted to examine whether pooled correlations differed across types of 
inhibitory (SICI, LICI, cSP, and iSP) and facilitatory measures (ICF and SICF), as well as by physical 
activity assessment method (self-reported vs. device-based).

*Meta-analysis: Subgroup analyses*
*Inhibition*
```{r Subgroup analysis by inhibitory measure using metafor}
inhibition_tms_subg <- run_subgroup_analysis_metafor(inhibition_r, "inhibitory.measure")
summary(inhibition_tms_subg)
```
```{r inhibition by measure type meta, warning=FALSE}
inhibition_measure_type <- update(m.inhibition, subgroup = inhibitory.measure, tau.common = TRUE)
inhibition_measure_type
```
```{r Forest plot for inhibition type using meta, fig.height=10, fig.width=14}
create_forest_plot(inhibition_measure_type)
```

*Inhibition measure type: Save plot*
```{r Forest plot inhibition type export SVG, echo=TRUE}
save_forest_plot_svg(inhibition_measure_type, "forest_plot_inhibition-measure", height = 10, width = 14)
```

*Facilitation*
```{r Subgroup analysis by health status using metafor}
facilitation_type <- run_subgroup_analysis_metafor(facilitation_r, "facilitatory.measure")
summary(facilitation_type)
```
```{r facilitation type meta, warning=FALSE}
facilitation_measure_type <- update(m.facilitation, subgroup = facilitatory.measure, tau.common = TRUE)
facilitation_measure_type
```
```{r Forest plot for facilitation type meta, fig.height=7, fig.width=14}
create_forest_plot(facilitation_measure_type)
```

*Facilitation by tms measure type: Save plot*
```{r Forest plot facilitation type SVG, echo=TRUE}
save_forest_plot_svg(facilitation_measure_type, "forest_plot_facilitation-type", height = 7, width = 14)
```

## Meta-Regressions
Meta-regression analyses were conducted to examine whether study-level characteristics, including 
mean age and proportion of women were associated with the reported correlations.

*Meta Regressions*
*Excitability*
*Meta-regressions by proportion of women*
```{r Meta-regression by proportion of women excitability}
m.cor.reg.excitability.women <- metareg(m.excitability, ~Prop_women)
m.cor.reg.excitability.women
```

*Meta-regressions by age*
```{r Meta-regression by age excitability}
m.cor.reg.excitability.age <- metareg(m.excitability, ~Age)
m.cor.reg.excitability.age
```

*Meta-regressions by study quality*
```{r Meta-regression by study quality excitability}
m.cor.reg.excitability.quality <- metareg(m.excitability, ~Q_score)
m.cor.reg.excitability.quality
```

*Inhibition*
*Meta-regressions by proportion of women*
```{r Meta-regression by proportion of women inhibition}
m.cor.reg.inhibition.women <- metareg(m.inhibition, ~Prop_women)
m.cor.reg.inhibition.women
```

*Meta-regressions by age*
```{r Meta-regression by age inhibition}
m.cor.reg.inhibition.age <- metareg(m.inhibition, ~Age)
m.cor.reg.inhibition.age
```

*Meta-regressions by study quality*
```{r Meta-regression by study quality inhibition}
m.cor.reg.inhibition.quality <- metareg(m.inhibition, ~Q_score)
m.cor.reg.inhibition.quality
```

*Facilitation*
*Meta-regressions by proportion of women*
```{r Meta-regression by proportion of women facilitation}
m.cor.reg.facilitation.women <- metareg(m.facilitation, ~Prop_women)
m.cor.reg.facilitation.women
```

*Meta-regressions by age*
```{r Meta-regression by age facilitation}
m.cor.reg.facilitation.age <- metareg(m.facilitation, ~Age)
m.cor.reg.facilitation.age
```

## Sensitivity Analysis
A  sensitivity  analysis  was  conducted  to  examine  whether  the  quality  of  the  studies  affected  the 
results. 

*Meta-regressions by study quality*
```{r Meta-regression by study quality facilitation}
m.cor.reg.facilitation.quality <- tryCatch(
  metareg(m.facilitation, ~Q_score),
  error = function(e) {
    message("[meta-regression error] ", conditionMessage(e))
    list(error = TRUE, message = conditionMessage(e)) # Placeholder object to indicate an error occurred
  }
)

if (is.list(m.cor.reg.facilitation.quality)
    && !is.null(m.cor.reg.facilitation.quality$error)
    && m.cor.reg.facilitation.quality$error) {
  cat("Meta-regression (facilitation ~ Q_score) failed: ", m.cor.reg.facilitation.quality$message, "\n")
} else {
  m.cor.reg.facilitation.quality
}
```

### Equivalence Testing
When  the  results  of  the  meta-analysis  were  not  statistically  significant,  equivalence  testing  was 
conducted  using  the  two  one-sided  tests  procedure  implemented  in  the  TOSTER  package  (24)  to 
determine  whether  pooled  correlations  were  statistically  equivalent  to  zero  within  prespecified 
equivalence bounds. Because no theoretically justified smallest effect size of interest could be identified, 
equivalence tests were conducted using bounds corresponding to a small correlation (r = ±0.10) (25). 
These bounds were converted to Fisher’s z to match the metric used in the meta-analysis. The pooled 
correlation  was  considered  statistically  equivalent  to  zero  and  practically  negligible  when  the  90% 
confidence interval of the pooled effect fell entirely within the equivalence bounds.

*Equivalence Testing*
*Excitability*
```{r Equivalence testing excitability}
run_equivalence_test(effect_size = -0.0063, se = 0.0548, sesoi_r = 0.1)
```

To evaluate  whether  the  association  could  be  considered  practically  negligible,  an 
equivalence test was conducted using equivalence bounds corresponding to a small effect size (−0.10 to 0.10).  The  equivalence  test  was  significant  (Z  =  1.66,  p  = 0.049),  and  the  90%  confidence  interval (−0.100 to 0.042) fell entirely within the predefined equivalence bounds, supporting the conclusion that the association between physical activity and corticospinal excitability is negligible.

*Inhibition*
```{r Equivalence testing inhibition}
run_equivalence_test(effect_size = 0.0237, se = 0.0597, sesoi_r = 0.1) #Timothée, mettre à jour les valeurs d'effect
```

The equivalence test was not significant (Z = −1.28, p = 0.100), and the 90% confidence interval (−0.074 to 0.122) extended beyond the predefined equivalence bounds. Thus, equivalence could not be concluded.

*Facilitation*
```{r Equivalence testing facilitation}
run_equivalence_test(effect_size = 0.0674, se = 0.0520, sesoi_r = 0.1)
```

The equivalence test was not significant (Z = −0.63, p = 0.263), and the 90% confidence interval (−0.018 to 0.153) extended beyond the predefined equivalence bounds. Thus, equivalence could not be concluded.

### Publication Bias
Potential publication bias and small-study effects were assessed using contour-enhanced funnel plots 
and Egger’s regression tests. Funnel plots display the Fisher’s z-transformed correlations against their 
standard errors to allow visual inspection of asymmetry around the pooled effect size. Egger’s regression 
test  was  used  as  a  statistical  complement  to  the  visual  inspection  of  funnel  plots.  Because  no  direct 
implementation  exists  for  multilevel  meta-analytic  models,  the  test  was  conducted  using  a  meta-
regression approach in which the standard error of the effect size estimate was included as a predictor in 
the multilevel model (23).

*Publication bias analysis*
*Small-study effects*
*Funnel plot*
```{r Contour-enhanced funnel plot excitability, fig.height=6, fig.width=8}
create_funnel_plot(m.excitability, "Contour-Enhanced Funnel Plot (excitability)")
```
```{r Contour-enhanced funnel plot inhibition, fig.height=6, fig.width=8}
create_funnel_plot(m.inhibition, "Contour-Enhanced Funnel Plot (inhibition)")
```
```{r Save funnel plot}
save_funnel_plot_png(m.inhibition, "Funnel Plot", "Contour-Enhanced Funnel Plot (tms and Physical Activity)")
```
```{r Contour-enhanced funnel plot facilitation, fig.height=6, fig.width=8}
create_funnel_plot(m.facilitation, "Contour-Enhanced Funnel Plot (facilitation)")
```

*Egger's test*
There is no direct function to conduct Egger's test for multi-level model. Alternatively, we calculate it by using the standard errors of the effect size estimates as a predictor in the meta-regression. (see: https://rstudio-pubs-static.s3.amazonaws.com/814435_6401e0cceb0b410c8208642dc5ee07f0.html)

```{r Eggers test for excitability}
egger_excitability <- run_eggers_test(excitability_r)
egger_excitability
```
```{r Eggers test for inhibition}
egger_inhibition <- run_eggers_test(inhibition_r)
egger_inhibition
```
```{r Eggers test for facilitation}
egger_facilitation <- run_eggers_test(facilitation_r)
egger_facilitation
```

Potential publication bias and small-study effects were assessed using contour-enhanced funnel plots 
and Egger’s regression tests. Visual inspection of the funnel plots for corticospinal excitability, cortical 
inhibition, and cortical facilitation did not reveal substantial asymmetry around the pooled effect sizes.
Egger’s  regression  tests  conducted  using  the  meta-regression  approach  were  not  statistically 
significant  for  any  of  the  meta-analyses.  The  regression  coefficient  for  the  standard  error  was  not 
significant for corticospinal excitability (p = 0.86), cortical inhibition (p = 0.71), or cortical facilitation (p 
= 0.16). These results indicate that smaller studies did not systematically report larger effect sizes.


# References
- Strick PL, Dum RP, Rathelot JA. The cortical motor areas and the emergence of motor skills: a neuroanatomical  perspective.  Annu Rev Neurosci  44:  425–447,  2021.  doi:10.1146/annurev-neuro-070918-050216.
- Derosiere G, Duque J. Tuning the corticospinal system: how distributed brain circuits shape human actions. Neuroscientist 26: 359–379, 2020. doi:10.1177/1073858419896751.
- Pascual-Leone A, Amedi A, Fregni F, Merabet LB. The plastic human brain cortex. Annu Rev Neurosci 28: 377–401, 2005. doi:10.1146/annurev.neuro.27.070203.144216.
- Bull FC, Al-Ansari SS, Biddle S, Borodulin K, Buman MP, Cardon G, Carty C, Chaput JP, Chastin S, Chou R, Dempsey PC, DiPietro L, Ekelund U, Firth J, Friedenreich CM, Garcia L, Gichu  M,  Jago  R,  Katzmarzyk  PT,  Lambert  E,  Leitzmann  M,  Milton  K,  Ortega  FB, Ranasinghe C, Stamatakis E, Tiedemann A, Troiano RP, van der Ploeg HP, Wari V, Willumsen JF. World Health Organization 2020 guidelines on physical activity and sedentary behaviour. Br J Sports Med 54: 1451–1462, 2020. doi:10.1136/bjsports-2020-102955.
- Mellow ML, Goldsworthy MR, Coussens S, Smith AE. Acute aerobic exercise and neuroplasticity of  the  motor  cortex:  a  systematic  review.  J  Sci  Med  Sport  23:  408–414,  2020. doi:10.1016/j.jsams.2019.10.015.
- Youssef  L,  Harroum  N,  Francisco  BA,  Johnson  L,  Arvisais  D,  Pageaux  B,  Romain  AJ, Hayward KS, Neva JL. Neurophysiological effects of acute aerobic exercise in young adults: a systematic  review  and  meta-analysis.  Neurosci  Biobehav  Rev  164:  105811,  2024.  doi: 10.1016/j.neubiorev.2024.105811.
- Rasmussen P, Brassard P, Adser H, Pedersen MV, Leick L, Hart E, Secher NH, Pedersen BK, Pilegaard H.  Evidence  for  a  release  of  brain-derived  neurotrophic  factor  from  the  brain  during exercise. Exp Physiol 94: 1062–1069, 2009. doi:10.1113/expphysiol.2009.048512.
- Skriver K, Roig M, Lundbye-Jensen J, Pingel J, Helge JW, Kiens B, Nielsen JB. Acute exercise improves motor memory: exploring potential biomarkers. Neurobiol Learn Mem 116: 46–58, 2014. doi:10.1016/j.nlm.2014.08.004.
- El-Sayes J, Harasym D, Turco CV, Locke MB, Nelson AJ. Exercise-induced neuroplasticity: a mechanistic  model  and  prospects  for  promoting  plasticity.  Neuroscientist  25:  65–85,  2019. doi:10.1177/1073858418771538. 
- Cirillo J, Lavender AP, Ridding MC, Semmler JG. Motor cortex plasticity induced by paired associative stimulation is enhanced in physically active individuals. J Physiol 587: 5831–5842, 2009. doi:10.1113/jphysiol.2009.181834.
- Lulic T, El-Sayes J, Fassett HJ, Nelson AJ. Physical activity levels determine exercise-induced changes in brain excitability. PLoS One 12: e0173672, 2017. doi:10.1371/journal.pone.0173672.
- Kujirai T, Caramia MD, Rothwell JC, Day BL, Thompson PD, Ferbert A, Wroe S, Asselman P, Marsden CD.  Corticocortical  inhibition  in  human  motor  cortex.  J Physiol  471:  501–519,  1993. doi:10.1113/jphysiol.1993.sp019912.
- Ziemann U, Rothwell JC, Ridding MC. Interaction between intracortical inhibition and facilitation in human motor cortex. J Physiol 496: 873–881, 1996. doi:10.1113/jphysiol.1996.sp021734.
- Hupfeld KE, Swanson CW, Fling BW, Seidler RD.  TMS-induced  silent  periods:  A  review  of methods  and  call  for  consistency.  J  Neurosci  Methods  346:  108950,  2020. doi:10.1016/j.jneumeth.2020.108950.
- Page MJ, Moher D, Bossuyt PM, Boutron I, Hoffmann TC, Mulrow CD, Shamseer L, Tetzlaff JM, Akl EA, Brennan SE, Chou R, Glanville J, Grimshaw JM, Hróbjartsson A, Lalu MM, LiT, Loder EW, Mayo-Wilson E, McDonald S, McGuinness LA, Stewart LA, Thomas J, Tricco AC, Welch VA, Whiting P, McKenzie JE. PRISMA 2020 explanation and elaboration: updated guidance  and  exemplars  for  reporting  systematic  reviews.  BMJ  372:  n160,  2021. doi:10.1136/bmj.n160.
- Downs SH, Black N. The feasibility of creating a checklist for the assessment of the methodological quality both of randomised and non-randomised studies of health care interventions. J Epidemiol Community Health 52: 377–384, 1998. doi:10.1136/jech.52.6.377.
- R Core Team. R: a language and environment for statistical computing. R Foundation for Statistical Computing. Version 4.4.1 (software), 2024. R-project.org.
- Viechtbauer W. metafor: meta-analysis package for R. Version 4.6-0 (R package), 2023. Available from: https://cran.r-project.org/web/packages/metafor/metafor.pdf.
- Schwarzer G. meta: general package for meta-analysis. Version 8.1-0 (R package), 2023. Available from: https://cran.r-project.org/web/packages/meta.
- Viechtbauer  W.  Bias  and  efficiency  of  meta-analytic  variance  estimators  in  the  random-effects model. J Educ Behav Stat 30: 261–293, 2005. doi:10.3102/10769986030003261.
- Higgins  JPT,  Thompson  SG.  Quantifying  heterogeneity  in  a  meta-analysis.  Stat  Med  21: 1539–1558, 2022. doi:10.1002/sim.1186.
- Knapp G, Hartung J. Improved tests for a random effects meta-regression with a single covariate. Stat Med 22: 2693–2710, 2003. doi:10.1002/sim.1482.
- Egger M, Davey Smith G, Schneider M, Minder C. Bias in meta-analysis detected by a simple, graphical test. BMJ 315: 629–634, 1997. doi:10.1136/bmj.315.7109.62.
- Lakens D, Caldwell A. TOSTER: Two One-Sided Tests (TOST) equivalence testing. Version 0.8.4 (R package), 2025. Available from: https://cran.r-project.org/web/packages/TOSTER.
- Lakens D.  Equivalence  tests:  a  practical  primer  for  t  tests,  correlations,  and  meta-analyses.  Soc Psychol Personal Sci 8: 355–362, 2017. doi:10.1177/1948550617697177.
- McGregor KM, Zlatar Z, Kleim E, Sudhyadhom A, Bauer A, Phan S, Seeds L, Ford A, Manini TM, White KD, Kleim J, Crosson B. Physical activity and neural correlates of aging: a combined TMS/fMRI study. Behav Brain Res 222: 158–168, 2011. doi:10.1016/j.bbr.2011.03.042.
- McGregor KM, Nocera JR, Sudhyadhom A, Patten C, Manini TM, Kleim JA, Crosson B, Butler AJ. Effects of aerobic fitness on aging-related changes of interhemispheric inhibition and motor performance. Front Aging Neurosci 5: 66, 2013. doi:10.3389/fnagi.2013.00066.
- Hand BJ, Opie GM, Sidhu SK, Semmler JG. Motor cortex plasticity and visuomotor skill learning in upper and lower limbs of endurance-trained cyclists. Eur J Appl Physiol 122: 169–184, 2022a. doi:10.1007/s00421-021-04825-y.
- Houde F, Laroche S, Thivierge V, Martel M, Harvey MP, Daigle F, Olivares-Marchant A, Beaulieu LD, Leonard G. Transcranial magnetic stimulation measures in the elderly: reliability, smallest detectable change and the potential influence of lifestyle habits. Front Aging Neurosci 10: 379, 2018. doi:10.3389/fnagi.2018.00379.
- Smith AE, Dumuid D, Goldsworthy MR, Graetz L, Hodyl N, Thornton NLR, Ridding MC. Daily activities are associated with non-invasive measures of neuroplasticity in older adults. Clin Neurophysiol 132: 984–992, 2021. doi:10.1016/j.clinph.2021.01.016.
- Hassanlouei H, Sundberg CW, Smith AE, Kuplic A, Hunter SK.  Physical  activity  modulates corticospinal excitability of the lower limb in young and old adults. J Appl Physiol 123: 364–374,2017. doi:10.1152/japplphysiol.01078.2016.
- El-Sayes J, Turco CV, Skelly LE, Nicolini C, Fahnestock M, Gibala MJ, Nelson AJ. The effects of  biological  sex  and  ovarian  hormones  on  exercise-induced  neuroplasticity.  Neuroscience  410: 29–40, 2019. doi:10.1016/j.neuroscience.2019.04.054.
- Rozand V, Senefeld JW, Sundberg CW, Smith AE, Hunter SK. Differential effects of aging and physical activity on corticospinal excitability of upper and lower limb muscles. J Neurophysiol 122: 241–250, 2019. doi:10.1152/jn.00077.2019.
- Hu M, Zeng N, Gu Z, Zheng Y, Xu K, Xue L, Leng L, Lu X, Shen Y, Huang J. Short-term high-intensity  interval  exercise  promotes  motor  cortex  plasticity  and  executive  function  in  sedentary females. Front Hum Neurosci 15: 620958, 2021. doi:10.3389/fnhum.2021.620958.
- Hand BJ, Opie GM, Sidhu SK, Semmler JG.  Motor  cortex  plasticity  is  greater  in  endurance-trained  cyclists  following  acute  exercise.  J  Appl  Physiol  133:  932–944,  2022b. doi:10.1152/japplphysiol.00213.2022.
- Wang YR, Lefebvre G, Picard M, Lamoureux-Andrichuk A, Ferland MC, Therrien-Blanchet JM, Boré A, Tremblay J, Descoteaux M, Champoux F, Théoret H. Physiological, anatomical and metabolic  correlates  of  aerobic  fitness  in  human  primary  motor  cortex:  a  multimodal  study. Neuroscience 517: 70–83, 2023. doi:10.1016/j.neuroscience.2023.03.007.
- Curtin D, Cadwallader CJ, Taylor EM, Andrews SC, Stout JC, Hendrikse JJ, Chong TT, Coxon JP. Ageing attenuates exercise-enhanced motor cortical plasticity. J Physiol 601: 5733–5750, 2023. doi:10.1113/JP285243.
- Ross  RE,  Saladin  ME,  George  MS,  Gregory  CM.  Acute  effects  of  aerobic  exercise  on corticomotor plasticity in individuals with and without depression. J Psychiatr Res 176: 108–118, 2024. doi:10.1016/j.jpsychires.2024.06.002.
- Hougland  JR,  Proessl  F,  Meglino  N,  Canino  MC,  Sterczala  AJ,  Connaboy  C,  Nindl  BC, Flanagan SD. Agreement and consistency of absolute and relative corticospinal stimulus-response curves for upper, lower, and axial musculature in healthy adults. J Clin Neurophysiol 42: 264–271, 2025. doi:10.1097/WNP.0000000000001109.
- Digonet  G,  Lapole  T,  Gelebart  J,  Bouvier  J,  Blanco  L,  Magaud  J,  Pialoux  V,  Pingon  M, Stauffer  E,  Debarnot  U.  High-intensity  interval  exercise  affects  explicit  sequential  motor consolidation  with  both  physical  and  motor  imagery  practice.  Scand  J  Med  Sci  Sports  35(11): e70168, 2025. doi: 10.1111/sms.70168.
- Harroum N, O'Farrell A, Youssef L, Bohbot L, Maati H, Joubert M, Pageaux B, Neva JL. Motor cortical excitability and inhibition are differentially modulated by aerobic exercise intensity. Cereb Cortex 35(8): bhaf230, 2025. doi: 10.1093/cercor/bhaf230.
- Gamage  NN,  Liao  WY,  Atherton  PJ,  Piasecki  M,  Opie  GM,  Semmler  JG.  Transcranial alternating current stimulation improves ballistic motor performance in trained and untrained limbs of healthy older adults. Geroscience 48(2): 1589–1608, 2026. doi: 10.1007/s11357-025-02064-z.
- Farajzadeh  A,  Boisgontier  MP.  Dataset  physical  activity  and  TMS.  GitHub  2026. https://github.com/Boisgontier-Lab/Dataset-physical-activity-and-TMS
