---
title: "Meta-Analysis_TMS_Physical_Activity"
author: "IM Lahart, A Farajzadeh, MP Boisgontier"
date: "`r format(Sys.Date(),'%e de %B, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
---
<style>
body{
  font-size: 8pt;
}
</style>
---

# R Markdown file set-up and packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
installed.packages()[, c("Package", "Version")]
```

Packages required:
1) dmetar
2) tidyverse
3) meta
4) metafor
5) esc
6) TOSTER

```{r packages, include=FALSE}
# Source the package installation script
source("00_package_installation.R")

# Source custom functions
source("01_functions_preprocess.R")
source("02_functions_analysis.R")
source("03_functions_plots.R")
```


# Meta-analysis
All analyses were conducted in the R statistical environment (R Core Team, 2023) using the meta (Schwarzer, 2023) and metafor (Viechtbauer, 2010, 2023) packages.

Pearson product–moment correlations from eligible studies were pooled to examine the relationship between physical activity and transcranial magnetic stimulation (TMS) measures of cortico-spinal excitability, cortical inhibition, and cortical facilitation. Prior to analysis, correlations were Fisher’s z-transformed to stabilize variance, and the corresponding sampling variances were calculated. Pooled estimates were then converted back to Pearson correlations for ease of interpretation.

Meta-analyses were conducted using multilevel random-effects models implemented with the metafor R package (Viechtbauer, 2010, 2023). This approach accounts for statistical dependence among multiple correlation estimates reported within the same study. A multilevel approach was used because several studies contributed more than one correlation estimate (e.g., different TMS outcomes or measurement conditions), which introduces statistical dependence among effect sizes. Multilevel meta-analysis appropriately accounts for this dependency without requiring aggregation of effect sizes within studies. Specifically, correlation estimates were nested within studies, resulting in a three-level model (level 1: sampling variance, level 2: correlation estimates within studies, level 3: studies). Between-study heterogeneity was estimated using the restricted maximum likelihood (REML) estimator (Viechtbauer, 2005). Heterogeneity was quantified using the I² statistic, which represents the proportion of total variability in observed effect sizes that is not attributable to sampling error (Higgins & Thompson, 2002). Because a multilevel meta-analytic model was used, I² values were decomposed across variance components to estimate the proportion of variability attributable to differences between studies and between effect sizes within studies.

To reduce the risk of inflated type I error rates, confidence intervals for pooled estimates were calculated using a Knapp–Hartung adjustment (Knapp & Hartung, 2003). In addition to pooled correlations and their confidence intervals, prediction intervals were calculated to estimate the range within which the true effect size of a future study is expected to fall based on the current evidence. Unlike confidence intervals, which describe the precision of the pooled estimate, prediction intervals incorporate between-study heterogeneity and therefore reflect the expected variability of effects across future studies.

For visualization purposes, forest plots were produced using the meta R package (Schwarzer, 2023) with a RevMan-style layout. These plots were based on random-effects models equivalent to the multilevel analyses and were used solely for graphical presentation. Sensitivity analyses using conventional random-effects models were also conducted using the metacor function in the meta package.

Publication bias was visually assessed using contour-enhanced funnel plots, which display the Fisher’s z-transformed correlations against their standard errors. In the absence of publication bias, studies are expected to form a symmetrical inverted funnel around the pooled effect size.

Subgroup analyses were conducted to examine whether pooled correlations differed across types of inhibitory modulation (SICI, LICI, cSP, and iSP) and facilitatory modultation (ICF and SICF)

# Import Pearson r data

```{r import data files, include=FALSE}
excitability_r <- import_correlation_data("excitability.csv")
inhibition_r <- import_correlation_data("inhibition.csv")
facilitation_r <- import_correlation_data("facilitation.csv")
```

# Data file glimpse

```{r glimpse, include=FALSE}
glimpse(excitability_r)
glimpse(inhibition_r)
glimpse(facilitation_r)
```

# Calculating z and var.z 
```{r z and var.z calculation, include=FALSE}
excitability_r <- calculate_fisher_z(excitability_r)
inhibition_r <- calculate_fisher_z(inhibition_r)
facilitation_r <- calculate_fisher_z(facilitation_r)
```

## Excitability (CSE): Primary analysis of using metafor::rma.mv()
```{r primary excitability meta-analysis RE REML using metafor}
m.cor.excitability <- run_multilevel_meta(excitability_r)
summary(m.cor.excitability)
```

### Excitability (CSE): Converting Fisher's z back to Pearson's r

```{r Convert excitability Fisher z back to Pearsons r}
z_to_r(-0.0063)   # point estimate
z_to_r(-0.1239)   # lower CI
z_to_r(0.1113)    # Upper CI
```

### Excitability (CSE): Explore heterogeneity

```{r excitability Heterogeneity}
i2_excitability <- var.comp(m.cor.excitability)
summary(i2_excitability)
plot(i2_excitability)
```

ADD TEXT


## Excitability (CSE): Sensitivity analysis using meta::metacor()

```{r Primary excitability analysis using meta}
m.excitability <- run_sensitivity_meta(excitability_r, "Sensitivity meta-analysis: Excitability")
m.excitability
```




#Corticospinal excitability
A total of 15 correlation estimates from 14 studies (435 participants) were included in the meta-analysis examining the association between habitual physical activity and corticospinal excitability.
The multilevel random-effects meta-analysis indicated no significant association between physical activity and corticospinal excitability (r = −0.01, 95% CI [−0.12, 0.11], p = 0.91). The prediction interval ranged from −0.21 to 0.19, suggesting that the true effect in future studies is likely to fall within this range.
Between-study heterogeneity was low, with a total I² of 13.3%, indicating that most of the observed variability was attributable to sampling error rather than true differences between studies. Decomposition of variance components indicated that 13.31% of the total variability occurred between effect sizes within studies, whereas between-study heterogeneity was negligible.
To further evaluate whether the association could be considered practically negligible, a two one-sided tests (TOST) equivalence test was conducted using equivalence bounds corresponding to a small effect size (−0.10 to 0.10). The equivalence test was significant (Z = 1.72, p = 0.043), and the 90% confidence interval (−0.096 to 0.084) fell entirely within the predefined equivalence bounds, supporting the conclusion that the association between physical activity and corticospinal excitability is negligible.
Sensitivity analyses using a conventional random-effects model implemented with the metacor function produced virtually identical results (r = −0.01, 95% CI [−0.12, 0.11], p = 0.91), supporting the robustness of the findings.

## Excitability (CSE): Forest plot
```{r Forest plot excitability, fig.height=7, fig.width=14}
create_forest_plot(m.excitability)
```


Excitability (CSE): Save plot
```{r Forest plot excitability export SVG, echo=TRUE}
save_forest_plot_svg(m.excitability, "forest_plot_excitability")
```

## Inhibition (SICI, LICI, cSP, iSP): Primary analysis of using metafor::rma.mv()
```{r primary inhibition meta-analysis RE REML using metafor}
m.cor.inhibition <- run_multilevel_meta(inhibition_r)
summary(m.cor.inhibition)
```

### Inhibition (SICI, LICI, cSP, iSP): Converting Fisher's z back to Pearson's r

```{r Convert inhibition Fisher z back to Pearsons r}
z_to_r(0.1642)   # point estimate
z_to_r(0.0429)   # lower CI
z_to_r(0.2856)   # Upper CI
```

### Inhibition (SICI, LICI, cSP, iSP): Explore heterogeneity

```{r inhibition Heterogeneity}
i2_inhibition <- var.comp(m.cor.inhibition)
summary(i2_inhibition)
plot(i2_inhibition)
```

ADD TEXT


## Inhibition (SICI, LICI, cSP, iSP): Sensitivity analysis using meta::metacor()

```{r Primary inhibition analysis using meta}
m.inhibition <- run_sensitivity_meta(inhibition_r, "Sensitivity meta-analysis: Inhibition")
m.inhibition
```

#Cortical inhibition
A total of 14 correlation estimates from 11 studies (451 participants) were included in the meta-analysis examining the association between habitual physical activity and measures of cortical inhibition (SICI, LICI, cSP, and iSP).
The multilevel random-effects meta-analysis indicated a significant positive association between physical activity and cortical inhibition (r = 0.16, 95% CI [0.04, 0.28], p = 0.012). This effect corresponds to a small positive correlation, suggesting that higher levels of habitual physical activity are associated with greater cortical inhibitory processes.
Between-study heterogeneity was low, with a total I² of 16.18%, indicating that most of the variability in observed correlations was attributable to sampling error. Variance decomposition showed that 16.18% of the variability occurred between studies, while no meaningful heterogeneity was observed between effect sizes within studies.
Sensitivity analyses using a conventional random-effects model implemented with the metacor function yielded virtually identical results (r = 0.16, 95% CI [0.04, 0.28], p = 0.012), supporting the robustness of the findings. The prediction interval ranged from −0.05 to 0.36, indicating that although the overall association was positive, future studies could observe effects ranging from negligible to moderately positive.
Subgroup analyses examining differences across inhibitory mechanisms (SICI, LICI, cSP, and iSP) revealed no statistically significant differences between modulation types (Q = 2.95, df = 3, p = 0.085). Nevertheless, exploratory estimates suggested that the association was strongest for interhemispheric inhibition (iSP) (r ≈ 0.47) and smaller for SICI and cSP, while the estimate for LICI was close to zero.

## Inhibition (SICI, LICI, cSP, iSP): Forest plot
```{r Forest plot for inhibition, fig.height=7, fig.width=14}
create_forest_plot(m.inhibition)
```


Inhibition (SICI, LICI, cSP, iSP): Save plot
```{r Forest plot inhibition export SVG, echo=TRUE}
save_forest_plot_svg(m.inhibition, "forest_plot_inhibition")
```


## Facilitation (ICF, SICF): Primary analysis of using metafor::rma.mv()
```{r primary facilitation meta-analysis RE REML using metafor}
m.cor.facilitation <- run_multilevel_meta(facilitation_r)
summary(m.cor.facilitation)
```

### Facilitation (ICF, SICF): Converting Fisher's z back to Pearson's r

```{r Convert facilitation Fisher z back to Pearsons r}
z_to_r(0.0674)   # point estimate
z_to_r(-0.0449)  # lower CI
z_to_r(0.1797)   # Upper CI
```

### Facilitation (ICF, SICF): Explore heterogeneity

```{r facilitation Heterogeneity}
i2_facilitation <- var.comp(m.cor.facilitation)
summary(i2_facilitation)
plot(i2_facilitation)
```

ADD TEXT


## Facilitation (ICF, SICF): Sensitivity analysis using meta::metacor()

```{r Primary facilitation analysis using meta}
m.facilitation <- run_sensitivity_meta(facilitation_r, "Sensitivity meta-analysis: Facilitation")
m.facilitation
```

#Cortical Facilitation

The multilevel random-effects meta-analysis indicated no statistically significant association between physical activity and cortical facilitation (r = 0.07, 95% CI [−0.04, 0.18], p = 0.22). The prediction interval ranged from −0.04 to 0.18, suggesting that the true effect in future studies is likely to be small and could range from slightly negative to moderately positive.
No meaningful heterogeneity was observed across studies (I² = 0%), indicating that the variability in observed correlations was entirely attributable to sampling error. Variance decomposition confirmed that neither between-study nor within-study variance components contributed meaningfully to heterogeneity.
Sensitivity analyses using a conventional random-effects model implemented with the metacor function yielded virtually identical results (r = 0.07, 95% CI [−0.04, 0.18], p = 0.22), supporting the robustness of the findings.
To evaluate whether the association could be considered practically negligible, a two one-sided tests (TOST) equivalence test was conducted using equivalence bounds corresponding to a trivial effect size (−0.10 to 0.10). The equivalence test was not significant (Z = −0.63, p = 0.26), and the 90% confidence interval (−0.018 to 0.153) extended beyond the predefined equivalence bounds. Thus, equivalence could not be concluded. The conventional null hypothesis test was also non-significant (Z = 1.30, p = 0.20), indicating that the pooled association did not differ significantly from zero. Taken together, these results suggest that the available evidence is inconclusive regarding whether the true association is negligible or small.
Subgroup analyses comparing intracortical facilitation measures (ICF vs. SICF) showed no significant difference between modulation types (Q = 0.00, df = 1, p = 0.97). Exploratory subgroup estimates were similar for ICF (r ≈ 0.07) and SICF (r ≈ 0.06).

## Facilitation (ICF, SICF): Forest plot
```{r Forest plot facilitation, fig.height=7, fig.width=14}
create_forest_plot(m.facilitation)
```


Facilitation (ICF, SICF): Save plot
```{r Forest plot facilitation export SVG, echo=TRUE}
save_forest_plot_svg(m.facilitation, "forest_plot_facilitation")
```

# Meta-analysis: Subgroup analyses
## Inhibition

```{r Subgroup analysis by inhibitory measure using metafor}
inhibition_tms_subg <- run_subgroup_analysis_metafor(inhibition_r, "inhibitory.measure")
summary(inhibition_tms_subg)
```

ADD TEXT


```{r inhibition by measure type meta, warning=FALSE}
inhibition_measure_type <- update(m.inhibition, subgroup = inhibitory.measure, tau.common = TRUE)
inhibition_measure_type
```

ADD TEXT

```{r Forest plot for inhibition type using meta, fig.height=10, fig.width=14}
create_forest_plot(inhibition_measure_type)
```

Inhibition measure type: Save plot
```{r Forest plot inhibition type export SVG, echo=TRUE}
save_forest_plot_svg(inhibition_measure_type, "forest_plot_inhibition-measure", height = 10, width = 14)
```

## Facilitation

```{r Subgroup analysis by health status using metafor}
facilitation_type <- run_subgroup_analysis_metafor(facilitation_r, "facilitatory.measure")
summary(facilitation_type)
```


```{r facilitation type meta, warning=FALSE}
facilitation_measure_type <- update(m.facilitation, subgroup = facilitatory.measure, tau.common = TRUE)
facilitation_measure_type
```


```{r Forest plot for facilitation type meta, fig.height=7, fig.width=14}
create_forest_plot(facilitation_measure_type)
```

Facilitation by tms measure type: Save plot
```{r Forest plot facilitation type SVG, echo=TRUE}
save_forest_plot_svg(facilitation_measure_type, "forest_plot_facilitation-type", height = 7, width = 14)
```

#Meta Regressions
## Excitability
### Meta-regressions by proportion of women
```{r Meta-regression by proportion of women excitability}
m.cor.reg.excitability.women <- metareg(m.excitability, ~Prop_women)
m.cor.reg.excitability.women
```

### Meta-regressions by age
```{r Meta-regression by age excitability}
m.cor.reg.excitability.age <- metareg(m.excitability, ~Age)
m.cor.reg.excitability.age
```

### Meta-regressions by study quality
```{r Meta-regression by study quality excitability}
m.cor.reg.excitability.quality <- metareg(m.excitability, ~Q_score)
m.cor.reg.excitability.quality
```

## Inhibition
### Meta-regressions by proportion of women
```{r Meta-regression by proportion of women inhibition}
m.cor.reg.inhibition.women <- metareg(m.inhibition, ~Prop_women)
m.cor.reg.inhibition.women
```

### Meta-regressions by age
```{r Meta-regression by age inhibition}
m.cor.reg.inhibition.age <- metareg(m.inhibition, ~Age)
m.cor.reg.inhibition.age
```

### Meta-regressions by study quality
```{r Meta-regression by study quality inhibition}
m.cor.reg.inhibition.quality <- metareg(m.inhibition, ~Q_score)
m.cor.reg.inhibition.quality
```

## Facilitation
### Meta-regressions by proportion of women
```{r Meta-regression by proportion of women facilitation}
m.cor.reg.facilitation.women <- metareg(m.facilitation, ~Prop_women)
m.cor.reg.facilitation.women
```

### Meta-regressions by age
```{r Meta-regression by age facilitation}
m.cor.reg.facilitation.age <- metareg(m.facilitation, ~Age)
m.cor.reg.facilitation.age
```

### Meta-regressions by study quality
```{r Meta-regression by study quality facilitation}
m.cor.reg.facilitation.quality <- tryCatch(
  metareg(m.facilitation, ~Q_score),
  error = function(e) {
    message("[meta-regression error] ", conditionMessage(e))
    list(error = TRUE, message = conditionMessage(e)) # Placeholder object to indicate an error occurred
  }
)

if (is.list(m.cor.reg.facilitation.quality)
    && !is.null(m.cor.reg.facilitation.quality$error)
    && m.cor.reg.facilitation.quality$error) {
  cat("Meta-regression (facilitation ~ Q_score) failed: ", m.cor.reg.facilitation.quality$message, "\n")
} else {
  m.cor.reg.facilitation.quality
}
```

# Equivalence Testing
## Excitability
```{r Equivalence testing excitability}
run_equivalence_test(effect_size = -0.0063, se = 0.0548, sesoi_r = 0.1)
```

## Facilitation
```{r Equivalence testing facilitation}
run_equivalence_test(effect_size = 0.0674, se = 0.0520, sesoi_r = 0.1)
```


# Publication bias analysis
## Small-study effects
### Funnel plot 

```{r Contour-enhanced funnel plot excitability, fig.height=6, fig.width=8}
create_funnel_plot(m.excitability, "Contour-Enhanced Funnel Plot (excitability)")
```

```{r Contour-enhanced funnel plot inhibition, fig.height=6, fig.width=8}
create_funnel_plot(m.inhibition, "Contour-Enhanced Funnel Plot (inhibition)")
```


```{r Save funnel plot}
save_funnel_plot_png(m.inhibition, "Funnel Plot", "Contour-Enhanced Funnel Plot (tms and Physical Activity)")
```

```{r Contour-enhanced funnel plot facilitation, fig.height=6, fig.width=8}
create_funnel_plot(m.facilitation, "Contour-Enhanced Funnel Plot (facilitation)")
```

### Egger's test

There is no direct function to conduct Egger's test for multi-level model. Alternatively, we calculate it by using the standard errors of the effect size estimates as a predictor in the meta-regression. (see: https://rstudio-pubs-static.s3.amazonaws.com/814435_6401e0cceb0b410c8208642dc5ee07f0.html)

```{r Eggers test for excitability}
egger_excitability <- run_eggers_test(excitability_r)
egger_excitability
```


```{r Eggers test for inhibition}
egger_inhibition <- run_eggers_test(inhibition_r)
egger_inhibition
```


```{r Eggers test for facilitation}
egger_facilitation <- run_eggers_test(facilitation_r)
egger_facilitation
```
#Pulication Bias
Egger’s regression tests using the standard errors of the effect size estimates as a predictor in the meta-regression showed that the coefficient of the standard error was not significant for any of the metaanalyses (p > 0.164), confirming that the data in the funnel plot was symmetrical, suggesting the absence of publication bias.

# References
- Cohen J. Statistical power analysis for the behavioral sciences. 2nd ed.; 1988.  
- Egger M, Davey Smith G, Schneider M, Minder C. Bias in meta-analysis detected by a simple, graphical test. BMJ. 1997;315(7109):629-634. https://doi.org/10.1136/bmj.315.7109.62  
- Higgins JPT, Thompson SG. Quantifying heterogeneity in a meta-analysis. Stat Med. 2002;21(11):1539-1558. https://doi.org/10.1002/sim.1186 
- Knapp G, Hartung J. Improved tests for a random effects meta-regression with a single covariate. Stat Med. 2003;22(17):2693-2710. https://doi.org/10.1002/sim.1482  
- R Core Team. R: A language and environment for statistical computing [Computer software]. Version 4.3.1. Vienna, Austria: Foundation for Statistical Computing; 2023. https://www.r-project.org 
- Schwarzer G. Meta: General package for meta-analysis [R package]. Version 6.5-0; 2023. https://cran.r-project.org/web/packages/meta/meta.pdf 
- Simonsohn U, Nelson LD, Simmons JP. P-curve: A key to the file-drawer. J Exp Psychol Gen. 2014;143(2):534-547. http://doi.org/10.1037/a0033242  
- Viechtbauer W. Bias and efficiency of meta-analytic variance estimators in the random-effects model. J Educ Behav Stat. 2005;30(3):261-293. https://doi.org/10.3102/10769986030003261  
- Viechtbauer W. Conducting meta-analyses in R with the metafor package. J Stat Softw. 2010;36(3):1-48. https://doi.org/10.18637/jss.v036.i03  
- Viechtbauer W. Metafor: Meta-analysis package for R [R package]. Version 4.2-0; 2023. https://cran.r-pro-ject.org/web/packages/metafor/metafor.pdf  
- Viechtbauer, "W. (2023). Metafor: Meta-Analysis Package for R (Version 4.2-0) [R pakage]. https://cran.r-project.org/web/packages/metafor/metafor.pdf  